\documentclass{article}

\usepackage[left=1.25in,top=1.25in,right=1.25in,bottom=1.25in,head=1.25in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{verbatim,float,url,enumerate}
\usepackage{graphicx,subfigure,psfrag}
\usepackage{natbib,xcolor}
\usepackage{microtype}
\usepackage{tcolorbox}
\newtheorem{algorithm}{Algorithm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\newcommand{\minimize}{\mathop{\mathrm{minimize}}}
\newcommand{\maximize}{\mathop{\mathrm{maximize}}}
\newcommand{\st}{\mathop{\mathrm{subject\,\,to}}}

\def\R{\mathbb{R}}
\def\E{\mathbb{E}}
\def\P{\mathbb{P}}
\def\S{\mathbb{S}}
\def\Cov{\mathrm{Cov}}
\def\Var{\mathrm{Var}}
\def\half{\frac{1}{2}}
\def\sign{\mathrm{sign}}
\def\supp{\mathrm{supp}}
\def\th{\mathrm{th}}
\def\tr{\mathrm{tr}}
\def\dim{\mathrm{dim}}
\def\dom{\mathrm{dom}}

\begin{document}

\title{Tutorial 1}
\author{\Large Ben Ayad Ayoub}

\bigskip


\maketitle


\tableofcontents


\section{Convex sets}

\noindent
(a) Closed sets and convex sets. 
\begin{enumerate}[i.]
\item A polyhedron $\{x \in \R^n : Ax \leq b \}$, for some $A\in
  \R^{m\times  n},  b\in \R^m$, is both convex and closed.  
\item  Show that if $S_i \subseteq \R^n$, $i\in I$ is a collection of convex 
  sets, then their intersection $\cap_{i\in I} S_i$ is also convex.  Show that
  the same statement holds if we replace ``convex'' with ``closed''.  
\item Given an example of a closed set in $\R^2$ whose convex hull is not
  closed.  
\item Let $A\in\R^{m\times n}$. Show that if $S\subseteq \R^m$ is convex then
  so is $A^{-1}(S) =\{ x \in \R^n : Ax \in S\}$, which is called the preimage of
  $S$ under the map $A :\R^n  \to \R^m$. Show that the same statement holds if
  we replace  ``convex'' with ``closed''.   
\item Let $A\in\R^{m\times n}$.  Show that if $S\subseteq \R^n$ is convex then 
  so is $A(S) = \{ Ax : x \in S \}$, called the image of $S$ under $A$. 
\item  Give an example of a matrix $A\in\R^{m\times n}$ and a set $S\subseteq
  \R^n$ that is closed and convex but such that $A(S)$ is not closed.  
\end{enumerate}

\begin{tcolorbox}
Proofs:
\begin{enumerate}[i.]
\item Not difficult. 
\item By noting that $\{ x \in \R^n: Ax \leq b \} = \cap_{i=1}^n  \{x\in\R^n: a_i^\top x \leq b_i \}$, it is left to prove that each halfspace associated with $(a_i, b_i)$ is closed (resp. convex), then we can use the result established in the past item. As the convexity can be proved in a straightforward manner, we will only prove that: $ H = \{x\in\R^n: a_i^\top x \leq b_i \}$ is closed.

    Let $y_0 \in \bar{H}$, 
    
\item 
\item 
\item 
\end{enumerate}
\end{tcolorbox}



\section{Polyhedra}%
\label{sec:polyhedra}

\begin{enumerate}[i.]
\item Show that if $P \subseteq \R^n$ is a polyhedron, and $A \in \R^{m \times
    n}$, then $A(P)$ is a polyhedron. Hint: you may use the fact that 
  $$
  \text{$P \subseteq \R^{m+n}$ is a polyhedron} 
  \; \Rightarrow \;
  \text{$\{x\in \R^n : \text{$(x,y)\in P$ for some $y\in\R^m$}\}$ 
    is a polyhedron}.
  $$
\item Show that if $Q \subseteq \R^m$ is a polyhedron, and $A \in \R^{m \times
    n}$, then $A^{-1}(Q)$ is a polyhedron. 
\end{enumerate}


\begin{tcolorbox}
Proofs:\\

\begin{enumerate}[i.]
\item 
\item 
\item 
\item 
\item 
\end{enumerate}
\end{tcolorbox}





\section{Convex functions}




\bigskip
\noindent
(a) Let $f$ be twice differentiable, with $\mathrm{dom}(f)$ convex.
Prove that: \\

$f$ is convex $\iff (\nabla f(x) - \nabla f(y))^T (x-y) \geq 0,$ for all $x,y$. 


\bigskip
\noindent
(b) A function $f : \R^n \to \R$ is said to be {\it coercive} provided
that $f(x) \to \infty$ as $\|x\|_2 \to \infty$.  A key fact about coercive
functions is that they attain their infimums.  Prove that a twice
differentiable, strongly convex function is coercive and hence attains its
infimum. Hint: use Q3 part (b.iv).  

\bigskip
\noindent
(b) Prove that the maximum of a convex function over a bounded
polyhedron must occur at one of the vertices.

\begin{tcolorbox}
Proofs:\\
\begin{enumerate}[i.]
\item 
\item 
\item 
\item 
\item 
\end{enumerate}
\end{tcolorbox}


\section{Lipschitz gradients}


\bigskip
\noindent
Let $f$ be convex and twice continuously differentiable. We will show that the following statements are equivalent.
\begin{enumerate}[i.]
\item $\nabla f$ is Lipschitz with constant $L$;
\item $(\nabla f(x) - \nabla f(y))^T(x-y) \leq L \|x-y\|_2^2$ for all
  $x,y$; 
\item $\nabla^2 f(x) \preceq LI$ for all $x$;
\item $f(y) \leq f(x) + \nabla f(x)^T (y-x) + \frac{L}{2} \|y-x\|_2^2$
  for all $x,y$.
\end{enumerate}


\begin{tcolorbox}
Proofs:\\
\begin{enumerate}[i.]
\item 
\item 
\item 
\item 
\item 
\end{enumerate}
\end{tcolorbox}


\section{Strongly Convex Functions}
\bigskip
\noindent

Let $f$ be convex and twice continuously differentiable. We will show that the following statements are equivalent.
\begin{enumerate}[i.]
\item $f$ is strongly convex with constant $m$;
\item $(\nabla f(x) - \nabla f(y))^T(x-y) \geq m \|x-y\|_2^2$ for all
  $x,y$;
\item $\nabla^2 f(x) \succeq mI$ for all $x$;
\item $f(y) \geq f(x) + \nabla f(x)^T (y-x) + \frac{m}{2}
  \|y-x\|_2^2$ for all $x,y$.
\end{enumerate}

\begin{tcolorbox}
\textbf{Proofs:} 
\begin{enumerate}[i.]
\item 
\item 
\item 
\item 
\item 
\end{enumerate}
\end{tcolorbox}





\end{document}
